### 2024-11-26 paper/paper.qmd
Introduction Completed

---
title: "Understanding the Relationship between Attributes and Whether DIH Exists"
subtitle: "A Data Analysis of Facilities of Toronto Libraries"
author: "Yanzun Jiang"
thanks: "Code and data are available at: [https://github.com/Stary54264/relationship_between_attributes_and_whether_dih_exists_in_toronto_libraries](https://github.com/Stary54264/relationship_between_attributes_and_whether_dih_exists_in_toronto_libraries)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(rstanarm)
library(here)
library(knitr)
```

\newpage

# Introduction

Despite the growing importance of innovation hubs in the global economy, the factors influencing the presence of Designated Innovation Hubs (DIH) in facilities remain underexplored and needed to be filled. This paper seeks to identify the key factors that influence whether a library in Toronto has a DIH, focusing on attributes such as area size, the number of public parking spots, the number of workstations in the library, and the year the library was built.

To investigate these factors, a logistic regression model was utilized, which is ideal for predicting binary outcomes (the presence or absence of a DIH). This analysis aims to estimate the likelihood of a facility having a DIH based on these attributes. The dataset used in this study contains information on various libraries in Toronto. After data cleaning, relevant variables was selected to do data analysis. The logistic regression model will reveal how each attribute (area size, parking availability, number of workstations, and age of the building) impacts the presence of a DIH.

The estimand in this paper is the presence of a Designated Innovation Hub (DIH) in a library. However, accurately observing which libraries have a DIH is not straightforward due to several challenges faced by urban planners. They may not have access to complete or up-to-date information about all libraries. This lack of comprehensive data, combined with regional variations and different reporting standards, makes it difficult to directly know the presence of a DIH across all libraries. To address this issue, a logistic regression model was built, since it allows us to estimate the probability of a facility having a DIH based on key attributes available in the dataset. By doing so, we aim to provide urban planners with insights into which factors most strongly influence the presence of DIHs, despite the challenges in directly measuring this estimand.

Results

DIHs are vital in fostering entrepreneurship, driving economic development, and supporting technological advancements. Understanding the attributes that contribute to the likelihood of a library of having a DIH could provide valuable insights for urban planners and policymakers.

The remainder of this paper is structured as follows: @sec-data discusses the data used in this analysis, including an overview of the dataset and key descriptive statistics. @sec-model outlines the logistic regression model, its assumptions, and its interpretation. @sec-results presents the results of the model, including the significance of each attribute in predicting the presence of a DIH. @sec-discussion offers a discussion of the findings, examines how these attributes affect DIH presence, and lists some weakness of this analysis. Statistical analysis is performed using `R` [@r], with packages `tidyverse` [@tidyverse], `arrow` [@arrow], `janitor` [@janitor], `testthat` [@testthat], `rstanarm` [@rstanarm], `here` [@here], and `knitr` [@knitr].

# Data {#sec-data}

## Overview

Our data [@library].... Following @rohan, we consider...

Overview text

## Measurement

Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.

## Outcome variables

Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.

## Predictor variables

Add graphs, tables and text.

Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.

# Model {#sec-model}

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results {#sec-results}

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

first_model <- readRDS(file = here::here("models/model.rds"))
```

# Discussion {#sec-discussion}

## First discussion point

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

Please don't use these as sub-heading labels - change them to be what your point actually is.

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

## Diagnostics

\newpage

# References

### 2024-11-28 scripts/00-simulate_data.R
Deleted One Variable in the Dataset

@@ -17,7 +17,6 @@ set.seed(1125)
 
 # Create a dataset by randomly assigning states and parties to divisions
 simulated_data <- tibble(
-  name = rep("XXX", 50),
   area = round(rexp(50, 0.00005)),
   parking = round(rexp(50, 0.1)),
   dih = sample(c(0, 1), 50, replace = TRUE, p = c(0.7, 0.3)),

### 2024-11-28 scripts/01-test_simulated_data.R

@@ -10,6 +10,7 @@
 
 #### Workspace setup ####
 library(tidyverse)
+library(testthat)
 
 
 #### Test data ####
@@ -20,14 +21,9 @@ test_that("dataset has 50 rows", {
   expect_equal(nrow(data), 50)
 })
 
-# Test that the dataset has 6 columns
-test_that("dataset has 6 columns", {
-  expect_equal(ncol(data), 6)
-})
-
-# Test that the 'name' column is character type
-test_that("'name' is character", {
-  expect_true(all(is.character(data$name)))
+# Test that the dataset has 5 columns
+test_that("dataset has 5 columns", {
+  expect_equal(ncol(data), 5)
 })
 
 # Test that the 'area' column is numeric type

### 2024-11-28 scripts/03-clean_data.R

@@ -19,12 +19,11 @@ raw_data <- read_csv("data/01-raw_data/raw_data.csv")
 cleaned_data <- raw_data |>
   janitor::clean_names() |>
   filter(physical_branch == 1) |>
-  rename(name = branch_name,
-         area = square_footage,
+  rename(area = square_footage,
          parking = public_parking) |>
   mutate(parking = ifelse(parking == "shared", 0, as.numeric(parking)),
          year = 2024 - present_site_year) |>
-  select(name, area, parking, dih, workstations, year) |>
+  select(area, parking, dih, workstations, year) |>
   tidyr::drop_na()
 
 

### 2024-11-28 scripts/04-test_analysis_data.R

@@ -22,14 +22,9 @@ test_that("dataset has 100 rows", {
   expect_equal(nrow(data), 100)
 })
 
-# Test that the dataset has 6 columns
-test_that("dataset has 6 columns", {
-  expect_equal(ncol(data), 6)
-})
-
-# Test that the 'name' column is character type
-test_that("'name' is character", {
-  expect_true(all(is.character(data$name)))
+# Test that the dataset has 5 columns
+test_that("dataset has 5 columns", {
+  expect_equal(ncol(data), 5)
 })
 
 # Test that the 'area' column is numeric type

### 2024-11-28 paper/paper.qmd
Data Section Completed

@@
 ---
-title: "Understanding the Relationship between Attributes and Whether DIH Exists"
-subtitle: "A Data Analysis of Facilities of Toronto Libraries"
+title: "Understanding Factors That Affects the Existence of Digital Innovation Hubs"
+subtitle: "An Analysis of Toronto Libraries' Data"
 author: "Yanzun Jiang"
@@
 library(tidyverse)
+library(arrow)
 library(rstanarm)
 library(here)
-library(knitr)
+library(tinytable)
 ```
@@
 
-Despite the growing importance of innovation hubs in the global economy, the factors influencing the presence of Designated Innovation Hubs (DIH) in facilities remain underexplored and needed to be filled.
-This paper seeks to identify the key factors that influence whether a library in Toronto has a DIH, focusing on attributes such as area size, the number of public parking spots, the number of workstations in the library, and the year the library was built.
+Despite the growing importance of innovation hubs in the global economy, the factors influencing the presence of Digital Innovation Hubs (DIH) in facilities remain underexplored and needed to be filled.
+This paper seeks to identify the key factors that influence whether a library in Toronto has a DIH, focusing on attributes such as area size, the number of public parking spots, the number of workstations in the library, and the number of years from the library was built.
 
 To investigate these factors, a logistic regression model was utilized, which is ideal for predicting binary outcomes (the presence or absence of a DIH).
-This analysis aims to estimate the likelihood of a facility having a DIH based on these attributes.
+This analysis aims to estimate the likelihood of a library having a DIH based on these attributes.
 The dataset used in this study contains information on various libraries in Toronto.
@@
 The logistic regression model will reveal how each attribute (area size, parking availability, number of workstations, and age of the building) impacts the presence of a DIH.
-
-The estimand in this paper is the presence of a Designated Innovation Hub (DIH) in a library.
-However, accurately observing which libraries have a DIH is not straightforward due to several challenges faced by urban planners.
-They may not have access to complete or up-to-date information about all libraries.
-This lack of comprehensive data, combined with regional variations and different reporting standards, makes it difficult to directly know the presence of a DIH across all libraries.
-To address this issue, a logistic regression model was built, since it allows us to estimate the probability of a facility having a DIH based on key attributes available in the dataset.
-By doing so, we aim to provide urban planners with insights into which factors most strongly influence the presence of DIHs, despite the challenges in directly measuring this estimand.
 
@@
 @sec-discussion offers a discussion of the findings, examines how these attributes affect DIH presence, and lists some weakness of this analysis.
-Statistical analysis is performed using `R` [@r], with packages `tidyverse` [@tidyverse], `arrow` [@arrow], `janitor` [@janitor], `testthat` [@testthat], `rstanarm` [@rstanarm], `here` [@here], and `knitr` [@knitr].
+Statistical analysis is performed using `R` [@r], with packages `tidyverse` [@tidyverse], `arrow` [@arrow], `janitor` [@janitor], `testthat` [@testthat], `rstanarm` [@rstanarm], `here` [@here], and `tinytable` [@tinytable].
+
+## Estimand
+
+The estimand in this paper is the presence of a Digital Innovation Hub (DIH) in a library.
+However, accurately observing which libraries have a DIH is not straightforward due to several challenges faced by urban planners.
+They may not have access to complete or up-to-date information about all libraries.
+This lack of comprehensive data, combined with regional variations and different reporting standards, makes it difficult to directly know the presence of a DIH across all libraries.
+To address this issue, a logistic regression model was built, since it allows us to estimate the probability of a facility having a DIH based on key attributes available in the dataset.
+By doing so, we aim to provide urban planners with insights into which factors most strongly influence the presence of DIHs, despite the challenges in directly measuring this estimand.
 
@@
 
+```{r}
+#| include: false
+#| warning: false
+#| message: false
+
+data <- read_parquet(
+  here::here("data/02-analysis_data/analysis_data.parquet"))
+```
+
 ## Overview
 
-Our data [@library].... Following @rohan, we consider...
-
-Overview text
+This report uses a dataset collected by Toronto Public Library [@library] and posted on Open Data Toronto [@data].
+[@tbl-data] is a preview of the dataset.
+These data provide valuable insights into the physical attributes and temporal characteristics of libraries that may house DIHs.
+Alternative datasets, such as those focusing on municipal buildings or educational institutions, were considered but ultimately not used because libraries are more accessible to public, thus having a bigger impact on the society.
+The dataset includes predictor variables including library area, public parking spots, the number of workstations, and the year the library was built.
+Data on these variables would be used to predict the outcome variable - the presence of DIHs.
 
@@
 
-## Outcome variables
+## Variables
 
-Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.
+One outcome variable and four predictor variables are used in the model:
 
-## Predictor variables
+`dih`: The presence of DIHs in libraries in Toronto. If there is one or more DIHs in the library, this field is set to 1; otherwise, this field is set to 0.
 
-Add graphs, tables and text.
+`area`: The total size of the library measured in square feet.
 
-Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.
+`parking`: The number of parking spaces available for the public. If a branch does not have any public parking spaces or shares parking spaces with another location, this field is set to 0.
+
+`workstations`: A count of computers with internet access available for public use in the branch.
+
+`year`: The number of years from the year that the present location of the library was officially opened to the general public.
+This variable was constructed using the formula $year=2024-year~built$.
+The age of the library was used instead of the year that the library was built since the age shows the degree of newness, which might affect the presence of DIHs.
+However, the year built is not that direct.
+
+Theeir descriptive statistics and graphs of their distribution is included in appendix (@sec-graph).
 
@@
 
-# Additional data details
+# Descriptive Statistics and Graphs of the Dataset {#sec-graph}
 
-# Model details {#sec-model-details}
+## Preview of the Dataset
 
-## Posterior predictive check
+```{r}
+#| label: tbl-data
+#| tbl-cap: "Preview of the Toronto Libraries Dataset"
+#| message: false
+#| echo: false
 
-## Diagnostics
+preview <- tt(head(data))
+preview
+```
+
+## Descriptive Statistics
+
+```{r}
+#| label: tbl-area
+#| tbl-cap: "Descriptive Statistics of `area`"
+#| message: false
+#| echo: false
+
+area <- tt(data |> summarize(Mean = round(mean(area), 1),
+                     Median = median(area),
+                     Minimum = min(area),
+                     Maximum = max(area),
+                     IQR = round(IQR(area), 1)))
+area
+```
+
+```{r}
+#| label: tbl-parking
+#| tbl-cap: "Descriptive Statistics of `parking`"
+#| message: false
+#| echo: false
+
+parking <- tt(data |> summarize(Mean = round(mean(parking), 1),
+                     Median = median(parking),
+                     Minimum = min(parking),
+                     Maximum = max(parking),
+                     IQR = round(IQR(parking), 1)))
+parking
+```
+
+```{r}
+#| label: tbl-workstations
+#| tbl-cap: "Descriptive Statistics of `workstations`"
+#| message: false
+#| echo: false
+
+workstations <- tt(data |> summarize(Mean = round(mean(workstations), 1),
+                     Median = median(workstations),
+                     Minimum = min(workstations),
+                     Maximum = max(workstations),
+                     IQR = round(IQR(workstations), 1)))
+workstations
+```
+
+```{r}
+#| label: tbl-year
+#| tbl-cap: "Descriptive Statistics of `year`"
+#| message: false
+#| echo: false
+
+year <- tt(data |> summarize(Mean = round(mean(year), 1),
+                     Median = median(year),
+                     Minimum = min(year),
+                     Maximum = max(year),
+                     IQR = round(IQR(year), 1)))
+year
+```
+
+## Graphs
+
+```{r}
+#| label: fig-dih
+#| tbl-cap: "Presence of DIHs in Toronto Libraries"
+#| message: false
+#| echo: false
+
+data |> ggplot(aes(x = dih)) +
+  geom_bar(col = "lightblue", fill = "lightblue", alpha = 0.8) +
+  labs(x = "Presence of DIHs", y = "# of Libraries") +
+  theme_minimal()
+```
+
+```{r}
+#| label: fig-area
+#| tbl-cap: "Distribution of Total Areas of Libraries in Toronto"
+#| message: false
+#| echo: false
+
+data |> ggplot(aes(x = area)) +
+  geom_histogram(col = "lightblue", fill = "lightblue", alpha = 0.8) +
+  labs(x = "Total Area", y = "# of Libraries") +
+  theme_minimal()
+```
+
+```{r}
+#| label: fig-parking
+#| tbl-cap: "Distribution of Number of Parking Spaces at Libraries in Toronto"
+#| message: false
+#| echo: false
+
+data |> ggplot(aes(x = parking)) +
+  geom_histogram(col = "lightblue", fill = "lightblue", alpha = 0.8) +
+  labs(x = "# of Parking Spaces", y = "# of Libraries") +
+  theme_minimal()
+```
+
+```{r}
+#| label: fig-workstations
+#| tbl-cap: "Distribution of Number of Workstations in Libraries in Toronto"
+#| message: false
+#| echo: false
+
+data |> ggplot(aes(x = workstations)) +
+  geom_histogram(col = "lightblue", fill = "lightblue", alpha = 0.8) +
+  labs(x = "# of Workstations", y = "# of Libraries") +
+  theme_minimal()
+```
+
+```{r}
+#| label: fig-year
+#| tbl-cap: "Distribution of Age of Libraries in Toronto"
+#| message: false
+#| echo: false
+
+data |> ggplot(aes(x = year)) +
+  geom_histogram(col = "lightblue", fill = "lightblue", alpha = 0.8) +
+  labs(x = "# of Workstations", y = "# of Libraries") +
+  theme_minimal()
+```
 

### 2024-11-28 scripts/05-model_data.R
Fixed Error in Model

@@ -25,7 +25,7 @@ model <- stan_glm(
     data = data,
     family = binomial(link = "logit"),
     prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_intercept = normal(location = -1, scale = 2.5, autoscale = TRUE),
+    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
     seed = 1125)
 
 

### 2024-11-30 paper/paper.qmd
Model Completed

@@
 
-Despite the growing importance of innovation hubs in the global economy, the factors influencing the presence of Digital Innovation Hubs (DIH) in facilities remain underexplored and needed to be filled.
+Despite the growing importance of innovation hubs in the global economy, the factors influencing the presence of Digital Innovation Hubs (DIH) in facilities remain under-explored and needed to be filled.
 This paper seeks to identify the key factors that influence whether a library in Toronto has a DIH, focusing on attributes such as area size, the number of public parking spots, the number of workstations in the library, and the number of years from the library was built.
@@
 
-## Overview
-
 This report uses a dataset collected by Toronto Public Library [@library] and posted on Open Data Toronto [@data].
@@
 Data on these variables would be used to predict the outcome variable - the presence of DIHs.
-
-## Measurement
-
-Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.
 
@@
 
-Theeir descriptive statistics and graphs of their distribution is included in appendix (@sec-graph).
+Their descriptive statistics and graphs of their distribution is included in @sec-dsg.
+
+## Measurement
+
+The library dataset used in this study was collected through a combination of administrative records and self-reported surveys.
+While the dataset provides valuable insights, several factors need to be considered:
+
+Reporting Variability: Libraries differ in how they track and report operational data, leading to potential inconsistencies.
+For instance, “workstations” might only include computers in some libraries, while others might also count other types of technological infrastructure.
+
+Survey Limitations: The presence of a DIH was self-reported, which could result in over- or under-representation of actual DIHs.
+Some respondents might interpret “Digital Innovation Hub” differently based on their regional or institutional context.
+
+Geographical Coverage: The dataset might not represent all regions equally. Libraries in rural areas may be underrepresented, impacting the generalization of the findings.
+
+### Connection with Real-World
+
+The dataset connects real-world phenomena to measurable entries. For example:
+
+`area`: The size of a library, measured in square feet, reflects its physical capacity to host community activities, including DIHs. Size of library would affect the presence of DIHs.
+
+`parking`: The number of parking spaces captures the the likelihood of a library being visited. If a library is more likely to be visited, it would have more facilities.
+
+`workstations`: Number of workstations symbolize a library's technological infrastructure - computers and other digital tools that enable public access to the internet, software, and other resources.
+Libraries with more computers is likely to have DIHs.
+
+`year`: Newer libraries are often designed to meet current technological needs, making them more suitable for DIHs.
+
+`dih`: The presence of a DIH at a library provides a learning opportunity for the public.
 
@@
 
-The goal of our modelling strategy is twofold. Firstly,...
+```{r}
+#| include: false
+#| warning: false
+#| message: false
 
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
+model <- readRDS(here::here("models/model.rds"))
+```
+
+In this analysis, a Bayesian logistic regression model was used to examine the relationship between the presence of a DIH in libraries and key library attributes. More details are included in @sec-md.
+
+Our assumptions include that samples could represent every library in Toronto, observations should be independent with each other, and no perfect multicollinearity between predictor variables.
+
+There are some limitations of our model.
+The model would be no longer valid if the actual underlying relationship between the predictor variables and the outcome variable is non-linear.
+Also, the predictor variables might not represent every aspect that would affect the presence of DIHs.
+
+Additional predictor variables include position of the library (longitude and latitude).
+However, while the position of the library could affect the presence of DIHs indeed, the longitude and latitude are not associated with it linearly.
 
@@
 
-Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
+Define $y_i$ as whether a library has a DIH (0 for no and 1 for yes) with probability $p_i$, so it follows a Bernoulli distribution.
+Then, the logistic link function of $p_i$ is a linear combination of the intercept - $\beta_0$, and the effects of the predictor variables - $\beta_1$, $\beta_2$, $\beta_3$, and $\beta_4$ times the predictor variables respectively.
 
 \begin{align} 
-y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_i + \gamma_i\\
-\alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta &\sim \mbox{Normal}(0, 2.5) \\
-\gamma &\sim \mbox{Normal}(0, 2.5) \\
-\sigma &\sim \mbox{Exponential}(1)
+y_i|p_i &\sim \mbox{Bern}(p_i) \\
+\mbox{logit}(p_i) &= \beta_0 + \beta_1 \times \mbox{area}_i + \beta_2 \times \mbox{parking}_i + \beta_3 \times \mbox{workstations}_i + \beta_4 \times \mbox{year}_i \\
+\beta_0 &\sim \mbox{Normal}(0, 2.5) \\
+\beta_1 &\sim \mbox{Normal}(0, 2.5) \\
+\beta_2 &\sim \mbox{Normal}(0, 2.5) \\
+\beta_3 &\sim \mbox{Normal}(0, 2.5) \\
+\beta_4 &\sim \mbox{Normal}(0, 2.5)
 \end{align}
 
-We run the model in R using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
+Since we have no prior information about any variable, the prior of the intercept and coefficients was set to a normal distribution with $\mu=0$ and $\sigma=2.5$.
+We run the model in R [@r] using the `rstanarm` package [@rstanarm].
 
-### Model justification
+## Model justification
 
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
+We propose the following hypotheses regarding how library attributes influence the likelihood of having DIHs.
 
-We can use maths by including latex between dollar signs, for instance $\theta$.
+`area`: We anticipate that larger libraries are more likely to host DIHs.
+Greater area reflects increased physical capacity, enabling libraries to allocate dedicated spaces for innovation and technology.
+
+`parking`: The number of parking spaces is expected to positively correlate with the presence of a DIH.
+Parking facilities make libraries more accessible to the public, encouraging diverse patronage and increasing community engagement.
+Libraries with better accessibility might be more willing to improve its facilities and might receive greater funding and community support, promoting the establishment of advanced facilities like DIHs.
+
+`workstations`: A strong positive relationship between the number of workstations and the presence of a DIH is expected.
+Workstations, representing technological infrastructure, are often central to the function of a DIH.
+Libraries with more workstations are likely equipped with the resources needed to support digital innovation and technological engagement.
+
+`year`: We hypothesize a negative relationship between years since built and the likelihood of having a DIH.
+Older libraries might lack modern infrastructure and technological resources necessary for a DIH, whereas recently built or renovated libraries are more likely to own technological innovations aligned with the concept of a DIH.
 
@@
 Our results are summarized in @tbl-modelresults.
-
-```{r}
-#| echo: false
-#| eval: true
-#| warning: false
-#| message: false
-
-first_model <- readRDS(file = here::here("models/model.rds"))
-```
 
@@
 
-# Descriptive Statistics and Graphs of the Dataset {#sec-graph}
+# Descriptive Statistics and Graphs of the Dataset {#sec-dsg}
 
@@
   geom_histogram(col = "lightblue", fill = "lightblue", alpha = 0.8) +
-  labs(x = "# of Workstations", y = "# of Libraries") +
+  labs(x = "Age", y = "# of Libraries") +
   theme_minimal()
 ```
+
+# Model Details {#sec-md}
+
+```{r}
+#| label: fig-posterior
+#| fig-cap: Posterior Distribution for the Logistic Regression Model 
+#| echo: false
+#| warning: false
+#| message: false
+
+pp_check(model) +
+  theme_minimal()
+```
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+
+pred <- fitted(model)
+RMSE <- round(sqrt(mean((data$dih - pred) ^ 2)), 3)
+```
+
+The distribution of posterior is shown in @fig-posterior, which aligns with the actual data.
+From the graph, we can see that more libraries does not have a DIH.
+The $RMSE$ for our model is about `r RMSE`, which is a quite small value, meaning the model fits the data quite well.
 

### 2024-12-01 paper/paper.qmd
Result Section Completed

@@
 library(here)
-library(tinytable)
+library(knitr)
+library(kableExtra)
+library(modelsummary)
+library(performance)
 ```
@@
 @sec-discussion offers a discussion of the findings, examines how these attributes affect DIH presence, and lists some weakness of this analysis.
-Statistical analysis is performed using `R` [@r], with packages `tidyverse` [@tidyverse], `arrow` [@arrow], `janitor` [@janitor], `testthat` [@testthat], `rstanarm` [@rstanarm], `here` [@here], and `tinytable` [@tinytable].
+@sec-appendix provides extra tables and graphs to further explain the findings in this paper.
+
+Statistical analysis is performed using `R` [@r], with packages `tidyverse` [@tidyverse], `arrow` [@arrow], `janitor` [@janitor], `testthat` [@testthat], `here` [@here], `modelsummary` [@modelsummary], `performance` [@performance], `knitr` [@knitr], `kableExtra` [@kableExtra], and `rstanarm` [@rstanarm].
 
@@
 
-In this analysis, a Bayesian logistic regression model was used to examine the relationship between the presence of a DIH in libraries and key library attributes. More details are included in @sec-md.
+In this analysis, a Bayesian logistic regression model was used to examine the relationship between the presence of a DIH in libraries and key library attributes.
 
@@
 The model would be no longer valid if the actual underlying relationship between the predictor variables and the outcome variable is non-linear.
-Also, the predictor variables might not represent every aspect that would affect the presence of DIHs.
+Also, the predictor variables might not follow normal distribution.
 
@@
 
-Our results are summarized in @tbl-modelresults.
+Our model results are summarized in @tbl-model.
+The findings align with our prior expectations in some degree and provide insights into the relationship between the predictor variables and the presence of DIHs.
+The intercept is negative, showing that more libraries do not have a DIH.
+The coefficient of `area` is 0, meaning the area of the library has litte effect on the outcome variable.
+The slope of `parking` and `workstations` are all positive, meaning a increase in them would lead to a higher likelihood of having DIHs.
+Rather, `year` has a negative slope, meaning older libraries are less likely to have a DIH, which aligns with our assumption.
+
+The $R^2$ for this model is quite small, meaning the model might not fit the data well.
+However, the $RMSE$ is also quite small, meaning the problem of overfit would not present in our model.
+More details are included in @sec-md.
+
+\clearpage
+
+```{r, fig.pos="H"}
+#| label: tbl-model
+#| tbl-cap: "Summary Statistics of the Logistic Regression Model"
+#| message: false
+#| warning: false
+#| echo: false
+
+modelsummary(model, output = "kableExtra")
+```
 
@@
 
-# Appendix {-}
+# Appendix {-#sec-appendix}
 
@@
 
-```{r}
+```{r, fig.pos="H"}
 #| label: tbl-data
@@
 
-preview <- tt(head(data))
-preview
+kable(head(data))
 ```
@@
 
-```{r}
+```{r, fig.pos="H"}
 #| label: tbl-area
@@
 
-area <- tt(data |> summarize(Mean = round(mean(area), 1),
+kable(data |> summarize(Mean = round(mean(area), 1),
                         Median = median(area),
@@
                         IQR = round(IQR(area), 1)))
-area
 ```
 
-```{r}
+```{r, fig.pos="H"}
 #| label: tbl-parking
@@
 
-parking <- tt(data |> summarize(Mean = round(mean(parking), 1),
+kable(data |> summarize(Mean = round(mean(parking), 1),
                         Median = median(parking),
@@
                         IQR = round(IQR(parking), 1)))
-parking
 ```
 
-```{r}
+```{r, fig.pos="H"}
 #| label: tbl-workstations
@@
 
-workstations <- tt(data |> summarize(Mean = round(mean(workstations), 1),
+kable(data |> summarize(Mean = round(mean(workstations), 1),
                         Median = median(workstations),
@@
                         IQR = round(IQR(workstations), 1)))
-workstations
 ```
 
-```{r}
+```{r, fig.pos="H"}
 #| label: tbl-year
@@
 
-year <- tt(data |> summarize(Mean = round(mean(year), 1),
+kable(data |> summarize(Mean = round(mean(year), 1),
                         Median = median(year),
@@
                         IQR = round(IQR(year), 1)))
-year
 ```
@@
 
-```{r}
+From @fig-dih, we could see that more libraries do not have a DIH.
+All predictor variables are right-skewed (@fig-area, @fig-parking, and @fig-workstations), except `year` (@fig-year).
+`year` might follows a normal distribution, while other predictor variables might follows an exponential distribution.
+
+```{r, fig.pos="H"}
 #| label: fig-dih
-#| tbl-cap: "Presence of DIHs in Toronto Libraries"
+#| fig-cap: "Presence of DIHs in Toronto Libraries"
 #| message: false
@@
 
-```{r}
+```{r, fig.pos="H"}
 #| label: fig-area
-#| tbl-cap: "Distribution of Total Areas of Libraries in Toronto"
+#| fig-cap: "Distribution of Total Areas of Libraries in Toronto"
 #| message: false
@@
   geom_histogram(col = "lightblue", fill = "lightblue", alpha = 0.8) +
-  labs(x = "Total Area", y = "# of Libraries") +
+  labs(x = "Total Area of the Library", y = "# of Libraries") +
   theme_minimal()
@@
 
-```{r}
+```{r, fig.pos="H"}
 #| label: fig-parking
-#| tbl-cap: "Distribution of Number of Parking Spaces at Libraries in Toronto"
+#| fig-cap: "Distribution of Number of Parking Spaces at Libraries in Toronto"
 #| message: false
@@
   geom_histogram(col = "lightblue", fill = "lightblue", alpha = 0.8) +
-  labs(x = "# of Parking Spaces", y = "# of Libraries") +
+  labs(x = "# of Parking Spaces in the Library", y = "# of Libraries") +
   theme_minimal()
@@
 
-```{r}
+```{r, fig.pos="H"}
 #| label: fig-workstations
-#| tbl-cap: "Distribution of Number of Workstations in Libraries in Toronto"
+#| fig-cap: "Distribution of Number of Workstations in Libraries in Toronto"
 #| message: false
@@
   geom_histogram(col = "lightblue", fill = "lightblue", alpha = 0.8) +
-  labs(x = "# of Workstations", y = "# of Libraries") +
+  labs(x = "# of Workstations in the Library", y = "# of Libraries") +
   theme_minimal()
@@
 
-```{r}
+```{r, fig.pos="H"}
 #| label: fig-year
-#| tbl-cap: "Distribution of Age of Libraries in Toronto"
+#| fig-cap: "Distribution of Age of Libraries in Toronto"
 #| message: false
@@
   geom_histogram(col = "lightblue", fill = "lightblue", alpha = 0.8) +
-  labs(x = "Age", y = "# of Libraries") +
+  labs(x = "Age of the Library", y = "# of Libraries") +
   theme_minimal()
@@
 
-```{r}
+## Distribution of Posterior
+
+The distribution of posterior is shown in @fig-posterior, which aligns with the actual data. From the graph, we can see that more libraries does not have a DIH.
+
+```{r, fig.pos="H"}
 #| label: fig-posterior
-#| fig-cap: Posterior Distribution for the Logistic Regression Model 
+#| fig-cap: "Posterior Distribution for the Logistic Regression Model"
 #| echo: false
@@
 
-```{r}
+## Density Plots
+
+From @fig-area-dih, we could see that smaller libraries are likely to have no DIHs, while larger libraries are not sure to have DIHs.
+In @fig-parking-dih and @fig-workstations-dih, libraries with more parking spaces and workstations tends to have a DIH.
+On the opposite, the pattern shown in @fig-year-dih tells us older libraries tend to have no DIH.
+
+```{r, fig.pos="H"}
+#| label: fig-area-dih
+#| tbl-cap: "Density of `area` Categorized by Presence of DIHs"
+#| message: false
 #| echo: false
-#| warning: false
-#| message: false
 
-pred <- fitted(model)
-RMSE <- round(sqrt(mean((data$dih - pred) ^ 2)), 3)
+data |> ggplot(aes(x = area, fill = as.factor(dih))) +
+  geom_density(alpha = 0.5) +
+  labs(x = "Total Area of the Library", y = "Density", 
+       fill = "Presence of DIHs (0 = No, 1 = Yes)") +
+  theme_minimal()
 ```
 
-The distribution of posterior is shown in @fig-posterior, which aligns with the actual data.
-From the graph, we can see that more libraries does not have a DIH.
-The $RMSE$ for our model is about `r RMSE`, which is a quite small value, meaning the model fits the data quite well.
+```{r, fig.pos="H"}
+#| label: fig-parking-dih
+#| tbl-cap: "Density of `parking` Categorized by Presence of DIHs"
+#| message: false
+#| echo: false
+
+data |> ggplot(aes(x = parking, fill = as.factor(dih))) +
+  geom_density(alpha = 0.5) +
+  labs(x = "# of Parking Spaces in the Library", y = "Density", 
+       fill = "Presence of DIHs (0 = No, 1 = Yes)") +
+  theme_minimal()
+```
+
+```{r, fig.pos="H"}
+#| label: fig-workstations-dih
+#| tbl-cap: "Density of `workstations` Categorized by Presence of DIHs"
+#| message: false
+#| echo: false
+
+data |> ggplot(aes(x = workstations, fill = as.factor(dih))) +
+  geom_density(alpha = 0.5) +
+  labs(x = "# of Workstations in the Library", y = "Density", 
+       fill = "Presence of DIHs (0 = No, 1 = Yes)") +
+  theme_minimal()
+```
+
+```{r, fig.pos="H"}
+#| label: fig-year-dih
+#| tbl-cap: "Density of `year` Categorized by Presence of DIHs"
+#| message: false
+#| echo: false
+
+data |> ggplot(aes(x = year, fill = as.factor(dih))) +
+  geom_density(alpha = 0.5) +
+  labs(x = "Age of the Library", y = "Density", 
+       fill = "Presence of DIHs (0 = No, 1 = Yes)") +
+  theme_minimal()
+```
 

### 2024-12-01 paper/paper.qmd
Abstract Completed

@@
 date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "This study examines the factors influencing the presence of Digital Innovation Hubs (DIHs) in libraries, focusing on key attributes such as area, parking availability, workstations, and the age of the library.
+A logistic regression model is employed to analyze the relationship between these variables and the likelihood of a library hosting a DIH.
+The results indicate that higher parking and more workstations increase the likelihood of a library having a DIH, while older libraries are less likely to feature one.
+These findings can inform decisions on library resource allocation and the development of DIHs, particularly when planning for library renovations or new library constructions."
 format: pdf
@@
 Despite the growing importance of innovation hubs in the global economy, the factors influencing the presence of Digital Innovation Hubs (DIH) in facilities remain under-explored and needed to be filled.
+DIHs are vital in fostering entrepreneurship, driving economic development, and supporting technological advancements.
+Understanding the attributes that contribute to the likelihood of a library of having a DIH could provide valuable insights for urban planners and policymakers.
 This paper seeks to identify the key factors that influence whether a library in Toronto has a DIH, focusing on attributes such as area size, the number of public parking spots, the number of workstations in the library, and the number of years from the library was built.
@@
 
-Results
-
-DIHs are vital in fostering entrepreneurship, driving economic development, and supporting technological advancements.
-Understanding the attributes that contribute to the likelihood of a library of having a DIH could provide valuable insights for urban planners and policymakers.
+In our analysis, the logistic regression model reveals that libraries with higher parking and more workstations are more likely to have DIHs, while the area of the library has little effect on this outcome.
+Additionally, older libraries are less likely to feature a DIH, aligning with our expectations.
+The model's $R^2$ value suggests it does not fit the data very well, though the relatively low $RMSE$ indicates that overfitting is not a concern.
+These results provide valuable insights into the factors that influence the presence of DIHs in libraries.
 

### 2024-12-01 paper/paper.qmd
Modified Abstract

--- 2024-12-01 paper/paper.qmd
@@
 date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "This paper investigates what influences the presence of Digital Innovation Hubs (DIHs) in libraries, focusing on factors such as parking availability, workstations, library size, and age.
+Using a logistic regression model, we found that libraries with more parking and workstations are more likely to have DIHs, while older libraries are less likely to include them.
+These findings highlight the importance of modern facilities and adequate resources in fostering digital innovation within libraries.
+This research can guide library planners and policymakers in improving library services and ensuring access to technological opportunities for communities."
 format: pdf

### 2024-12-01 paper/paper.qmd
Fixed Errors in Caption

@@
 #| label: fig-area-dih
-#| tbl-cap: "Density of `area` Categorized by Presence of DIHs"
+#| fig-cap: "Density of `area` Categorized by Presence of DIHs"
 #| message: false
@@
 #| label: fig-parking-dih
-#| tbl-cap: "Density of `parking` Categorized by Presence of DIHs"
+#| fig-cap: "Density of `parking` Categorized by Presence of DIHs"
 #| message: false
@@
 #| label: fig-workstations-dih
-#| tbl-cap: "Density of `workstations` Categorized by Presence of DIHs"
+#| fig-cap: "Density of `workstations` Categorized by Presence of DIHs"
 #| message: false
@@
 #| label: fig-year-dih
-#| tbl-cap: "Density of `year` Categorized by Presence of DIHs"
+#| fig-cap: "Density of `year` Categorized by Presence of DIHs"
 #| message: false

### 2024-12-01 scripts/01-test_simulated_data.R
Fixed Errors

@@ -3,7 +3,6 @@
 # Author: Yanzun Jiang
 # Date: 25 November 2024
 # Contact: yanzun.jiang@mail.utoronto.ca
-# License: MIT
 # Pre-requisites: Should have simulated the dataset.
 # Any other information needed? None.
 

### 2024-12-01 scripts/02-download_data.R

@@ -3,7 +3,6 @@
 # Author: Yanzun Jiang
 # Date: 25 November 2024
 # Contact: yanzun.jiang@mail.utoronto.ca
-# License: MIT
 # Pre-requisites: None.
 # Any other information needed? None.
 

### 2024-12-01 scripts/03-clean_data.R

@@ -3,7 +3,6 @@
 # Author: Yanzun Jiang
 # Date: 25 November 2024
 # Contact: yanzun.jiang@mail.utoronto.ca
-# License: MIT
 # Pre-requisites: Should have downloaded the dataset.
 # Any other information needed? None.
 

### 2024-12-01 scripts/04-test_analysis_data.R

@@ -3,7 +3,6 @@
 # Author: Yanzun Jiang
 # Date: 25 November 2024
 # Contact: yanzun.jiang@mail.utoronto.ca
-# License: MIT
 # Pre-requisites: Should have downloaded and cleaned the dataset.
 # Any other information needed? None.
 

### 2024-12-01 scripts/05-model_data.R

@@ -4,7 +4,6 @@
 # Author: Yanzun Jiang
 # Date: 25 November 2024
 # Contact: yanzun.jiang@mail.utoronto.ca
-# License: MIT
 # Pre-requisites: Should have downloaded and cleaned the dataset.
 # Any other information needed? None.
 

### 2024-12-02 other/datasheet/datasheet.qmd
Datasheet Completed

---
title: "Datasheet for `data/02-analysis_data/analysis_data.parquet`"
author: "Yanzun Jiang"
thanks: "Code and data are available at: [https://github.com/Stary54264/relationship_between_attributes_and_whether_dih_exists_in_toronto_libraries](https://github.com/Stary54264/relationship_between_attributes_and_whether_dih_exists_in_toronto_libraries)."
date: today
date-format: long
format: pdf
number-sections: true
bibliography: references.bib
---

Extract of the questions from @datasheet.

**Motivation**

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
    - The dataset was created for the analysis of Toronto libraries. Using the dataset, we were able to build a model to analyze factors that affect the presence of DIHs in libraries. Few analysis was done to predict the presence of DIHs in libraries before.
2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
    - Yanzun Jiang. University of Toronto.
3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
    - No.
4. *Any other comments?*
    - No.

**Composition**

1. *What do the instances that comprise the dataset represent (for example, documents, photos, people, countries)? Are there multiple types of instances (for example, movies, users, and ratings; people and interactions between them; nodes and edges)? Please provide a description.*
    - Information about libraries in Toronto.
2. *How many instances are there in total (of each type, if appropriate)?*
	  - 100.
3. *Does the dataset contain all possible instances or is it a sample (not necessarily random) of instances from a larger set? If the dataset is a sample, then what is the larger set? Is the sample representative of the larger set (for example, geographic coverage)? If so, please describe how this representativeness was validated/verified. If it is not representative of the larger set, please describe why not (for example, to cover a more diverse range of instances, because instances were withheld or unavailable).*
	  - No, the larger set is all libraries. No, since the data only contains libraries in Toronto.
4. *What data does each instance consist of? "Raw" data (for example, unprocessed text or images) or features? In either case, please provide a description.*
	  - Total area of a library, number of parking spaces in a library, number of workstations in a library, age of a library, and presence of DIHs in a library.
5. *Is there a label or target associated with each instance? If so, please provide a description.*
	  - No.
6. *Is any information missing from individual instances? If so, please provide a description, explaining why this information is missing (for example, because it was unavailable). This does not include intentionally removed information, but might include, for example, redacted text.*
	  - No.
7. *Are relationships between individual instances made explicit (for example, users' movie ratings, social network links)? If so, please describe how these relationships are made explicit.*
	  - No.
8. *Are there recommended data splits (for example, training, development/validation, testing)? If so, please provide a description of these splits, explaining the rationale behind them.*
	  - No.
9. *Are there any errors, sources of noise, or redundancies in the dataset? If so, please provide a description.*
	  - No.
10. *Is the dataset self-contained, or does it link to or otherwise rely on external resources (for example, websites, tweets, other datasets)? If it links to or relies on external resources, a) are there guarantees that they will exist, and remain constant, over time; b) are there official archival versions of the complete dataset (that is, including the external resources as they existed at the time the dataset was created); c) are there any restrictions (for example, licenses, fees) associated with any of the external resources that might apply to a dataset consumer? Please provide descriptions of all external resources and any restrictions associated with them, as well as links or other access points, as appropriate.*
	  - It is self-contained.
11. *Does the dataset contain data that might be considered confidential (for example, data that is protected by legal privilege or by doctor-patient confidentiality, data that includes the content of individuals' non-public communications)? If so, please provide a description.*
	  - No.
12. *Does the dataset contain data that, if viewed directly, might be offensive, insulting, threatening, or might otherwise cause anxiety? If so, please describe why.*
	  - No.
13. *Does the dataset identify any sub-populations (for example, by age, gender)? If so, please describe how these subpopulations are identified and provide a description of their respective distributions within the dataset.*
	  - No.
14. *Is it possible to identify individuals (that is, one or more natural persons), either directly or indirectly (that is, in combination with other data) from the dataset? If so, please describe how.*
	  - No.
15. *Does the dataset contain data that might be considered sensitive in any way (for example, data that reveals race or ethnic origins, sexual orientations, religious beliefs, political opinions or union memberships, or locations; financial or health data; biometric or genetic data; forms of government identification, such as social security numbers; criminal history)? If so, please provide a description.*
	  - No.
16. *Any other comments?*
	  - No.

**Collection process**

1. *How was the data associated with each instance acquired? Was the data directly observable (for example, raw text, movie ratings), reported by subjects (for example, survey responses), or indirectly inferred/derived from other data (for example, part-of-speech tags, model-based guesses for age or language)? If the data was reported by subjects or indirectly inferred/derived from other data, was the data validated/verified? If so, please describe how.*
	  - The dataset was cleaned based on the raw dataset [@library] from Open Data Toronto [@data]. The data was validated.
2. *What mechanisms or procedures were used to collect the data (for example, hardware apparatuses or sensors, manual human curation, software programs, software APIs)? How were these mechanisms or procedures validated?*
	  - R [@r] was used to download the dataset. The code used to download it was provided on the website.
3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
	  - Convenience sampling.
4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
	  - Yanzun Jiang. No conpensation.
5. *Over what timeframe was the data collected? Does this timeframe match the creation timeframe of the data associated with the instances (for example, recent crawl of old news articles)? If not, please describe the timeframe in which the data associated with the instances was created.*
	  - Collected time: 2024.11.25. Creation time: ? - 2024.10.15
6. *Were any ethical review processes conducted (for example, by an institutional review board)? If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
	  - No.
7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
	  - Via third parties.
8. *Were the individuals in question notified about the data collection? If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
	  - NA.
9. *Did the individuals in question consent to the collection and use of their data? If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
	  - NA.
10. *If consent was obtained, were the consenting individuals provided with a mechanism to revoke their consent in the future or for certain uses? If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
	  - NA.
11. *Has an analysis of the potential impact of the dataset and its use on data subjects (for example, a data protection impact analysis) been conducted? If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
	  - No.
12. *Any other comments?*
	  - No.

**Preprocessing/cleaning/labeling**

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
	  - Yes.
2. *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
	  - Yes, `data/01-raw_data/raw_data.csv`.
3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
	  - Yes, R [@r] and tidyverse [@tidyverse] was used to clean the dataset
4. *Any other comments?*
	  - No.

**Uses**

1. *Has the dataset been used for any tasks already? If so, please provide a description.*
	  - No.
2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
	  - No.
3. *What (other) tasks could the dataset be used for?*
	  - Predict the presence of other facilities in libraries.
4. *Is there anything about the composition of the dataset or the way it was collected and preprocessed/cleaned/labeled that might impact future uses? For example, is there anything that a dataset consumer might need to know to avoid uses that could result in unfair treatment of individuals or groups (for example, stereotyping, quality of service issues) or other risks or harms (for example, legal risks, financial harms)? If so, please provide a description. Is there anything a dataset consumer could do to mitigate these risks or harms?*
	  - No.
5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
	  - No.
6. *Any other comments?*
	  - No.

**Distribution**

1. *Will the dataset be distributed to third parties outside of the entity (for example, company, institution, organization) on behalf of which the dataset was created? If so, please provide a description.*
	  - Yes.
2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
	  - Through the link to Github.
3. *When will the dataset be distributed?*
	  - From now.
4. *Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)? If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
	  - No.
5. *Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
	  - No.
6. *Do any export controls or other regulatory restrictions apply to the dataset or to individual instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
	  - No.
7. *Any other comments?*
	  - No.

**Maintenance**

1. *Who will be supporting/hosting/maintaining the dataset?*
	  - Yanzun Jiang.
2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	  - [yanzun.jiang@mail.utoronto.ca](mailto:yanzun.jiang@mail.utoronto.ca).
3. *Is there an erratum? If so, please provide a link or other access point.*
    - No.
4. *Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)? If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
    - No.
5. *If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)? If so, please describe these limits and explain how they will be enforced.*
    - No.
6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
    - No.
7. *If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so? If so, please provide a description. Will these contributions be validated/verified? If so, please describe how. If not, why not? Is there a process for communicating/distributing these contributions to dataset consumers? If so, please provide a description.*
    - Create a fork of the repo.
8. *Any other comments?*
    - No.

\newpage

# References

### 2024-12-02 paper/paper.qmd
Discussion Completed

@@
 ---
-title: "Understanding Factors That Affects the Existence of Digital Innovation Hubs"
+title: "Understanding Factors That Affect the Existence of Digital Innovation Hubs"
 subtitle: "An Analysis of Toronto Libraries' Data"
@@
 format: pdf
+appendix: true
 toc: true
@@
 
-Despite the growing importance of innovation hubs in the global economy, the factors influencing the presence of Digital Innovation Hubs (DIH) in facilities remain under-explored and needed to be filled.
+Despite the growing importance of innovation hubs in the global economy, the factors influencing the presence of Digital Innovation Hubs (DIH) in facilities remain under-explored and need to be filled.
 DIHs are vital in fostering entrepreneurship, driving economic development, and supporting technological advancements.
-Understanding the attributes that contribute to the likelihood of a library of having a DIH could provide valuable insights for urban planners and policymakers.
-This paper seeks to identify the key factors that influence whether a library in Toronto has a DIH, focusing on attributes such as area size, the number of public parking spots, the number of workstations in the library, and the number of years from the library was built.
+Understanding the attributes contributing to the likelihood of a library having a DIH could provide clarity for urban planners and policymakers.
+This paper seeks to identify the key factors that influence whether a library in Toronto has a DIH, focusing on attributes such as area size, the number of public parking spots, the number of workstations in the library, and the number of years from when the library was built.
 
-To investigate these factors, a logistic regression model was utilized, which is ideal for predicting binary outcomes (the presence or absence of a DIH).
+A logistic regression model was utilized to investigate these factors, which is ideal for predicting binary outcomes (the presence or absence of a DIH).
 This analysis aims to estimate the likelihood of a library having a DIH based on these attributes.
 The dataset used in this study contains information on various libraries in Toronto.
-After data cleaning, relevant variables was selected to do data analysis.
-The logistic regression model will reveal how each attribute (area size, parking availability, number of workstations, and age of the building) impacts the presence of a DIH.
+After data cleaning, relevant variables were selected to do data analysis.
+The logistic regression model will show how each attribute (area size, parking availability, number of workstations, and age of the building) impacts the presence of a DIH.
 
-In our analysis, the logistic regression model reveals that libraries with higher parking and more workstations are more likely to have DIHs, while the area of the library has little effect on this outcome.
+In our analysis, the logistic regression model shows that libraries with higher parking and more workstations are more likely to have DIHs, while the area of the library has little effect on this outcome.
 Additionally, older libraries are less likely to feature a DIH, aligning with our expectations.
 The model's $R^2$ value suggests it does not fit the data very well, though the relatively low $RMSE$ indicates that overfitting is not a concern.
-These results provide valuable insights into the factors that influence the presence of DIHs in libraries.
+These results provide clarity into the factors that influence the presence of DIHs in libraries.
 
@@
 @sec-results presents the results of the model, including the significance of each attribute in predicting the presence of a DIH.
-@sec-discussion offers a discussion of the findings, examines how these attributes affect DIH presence, and lists some weakness of this analysis.
-@sec-appendix provides extra tables and graphs to further explain the findings in this paper.
+@sec-discussion offers a discussion of the findings, examines how these attributes affect DIH presence, and lists some limitations of this analysis.
 
@@
 They may not have access to complete or up-to-date information about all libraries.
-This lack of comprehensive data, combined with regional variations and different reporting standards, makes it difficult to directly know the presence of a DIH across all libraries.
+This lack of data, combined with regional variations and different reporting standards, makes it difficult to directly know the presence of a DIH across all libraries.
 To address this issue, a logistic regression model was built, since it allows us to estimate the probability of a facility having a DIH based on key attributes available in the dataset.
-By doing so, we aim to provide urban planners with insights into which factors most strongly influence the presence of DIHs, despite the challenges in directly measuring this estimand.
+By doing so, we aim to provide urban planners with clarity into which factors most strongly influence the presence of DIHs, despite the challenges in directly measuring this estimand.
 
@@
 
-This report uses a dataset collected by Toronto Public Library [@library] and posted on Open Data Toronto [@data].
+This report uses a dataset collected by the Toronto Public Library [@library] and posted on Open Data Toronto [@data].
 [@tbl-data] is a preview of the dataset.
-These data provide valuable insights into the physical attributes and temporal characteristics of libraries that may house DIHs.
-Alternative datasets, such as those focusing on municipal buildings or educational institutions, were considered but ultimately not used because libraries are more accessible to public, thus having a bigger impact on the society.
+These data provide clarity into the physical attributes and temporal characteristics of libraries that may house DIHs.
+Alternative datasets, such as those focusing on municipal buildings or educational institutions, were considered but ultimately not used because libraries are more accessible to the public, thus having a bigger impact on society.
 The dataset includes predictor variables including library area, public parking spots, the number of workstations, and the year the library was built.
@@
 
-Their descriptive statistics and graphs of their distribution is included in @sec-dsg.
+Their descriptive statistics and graphs of their distribution are included in @sec-dsg.
 
@@
 
-The library dataset used in this study was collected through a combination of administrative records and self-reported surveys.
-While the dataset provides valuable insights, several factors need to be considered:
+The library dataset used in this study was collected by Open Data Toronto [@data]. While the dataset provides clarity, several factors need to be considered:
 
@@
 
-Survey Limitations: The presence of a DIH was self-reported, which could result in over- or under-representation of actual DIHs.
-Some respondents might interpret “Digital Innovation Hub” differently based on their regional or institutional context.
-
-Geographical Coverage: The dataset might not represent all regions equally. Libraries in rural areas may be underrepresented, impacting the generalization of the findings.
+Geographical Coverage: The dataset might not represent all regions equally.
+Libraries in rural areas may be underrepresented since their information might be inaccurate and hard to access, impacting the generalization of the findings.
 
@@
 
-`area`: The size of a library, measured in square feet, reflects its physical capacity to host community activities, including DIHs. Size of library would affect the presence of DIHs.
+`area`: The size of a library, measured in square feet, reflects its physical capacity to host community activities, including DIHs. The size of the library would affect the presence of DIHs.
 
-`parking`: The number of parking spaces captures the the likelihood of a library being visited. If a library is more likely to be visited, it would have more facilities.
+`parking`: The number of parking spaces captures the likelihood of a library being visited, and this would affect the facilities in it.
 
-`workstations`: Number of workstations symbolize a library's technological infrastructure - computers and other digital tools that enable public access to the internet, software, and other resources.
-Libraries with more computers is likely to have DIHs.
+`workstations`: The number of workstations symbolizes a library's technological infrastructure - computers and other digital tools that enable public access to the internet, software, and other resources
 
-`year`: Newer libraries are often designed to meet current technological needs, making them more suitable for DIHs.
+`year`: Newer libraries are often designed to meet current technological needs.
 
@@
 
-Our assumptions include that samples could represent every library in Toronto, observations should be independent with each other, and no perfect multicollinearity between predictor variables.
+Our assumptions include that samples could represent every library in Toronto, observations should be independent of each other, and no perfect multicollinearity between predictor variables.
 
@@
 The model would be no longer valid if the actual underlying relationship between the predictor variables and the outcome variable is non-linear.
-Also, the predictor variables might not follow normal distribution.
+Also, the predictor variables might not follow the normal distribution.
 
-Additional predictor variables include position of the library (longitude and latitude).
+Additional predictor variables include the position of the library (longitude and latitude).
 However, while the position of the library could affect the presence of DIHs indeed, the longitude and latitude are not associated with it linearly.
@@
 
-Since we have no prior information about any variable, the prior of the intercept and coefficients was set to a normal distribution with $\mu=0$ and $\sigma=2.5$.
+Since we have no prior information about any variable, the prior of the intercept and coefficients were set to a normal distribution with $\mu=0$ and $\sigma=2.5$.
 We run the model in R [@r] using the `rstanarm` package [@rstanarm].
@@
 `area`: We anticipate that larger libraries are more likely to host DIHs.
-Greater area reflects increased physical capacity, enabling libraries to allocate dedicated spaces for innovation and technology.
+The greater area reflects increased physical capacity, enabling libraries to allocate dedicated spaces for innovation and technology.
 
@@
 Parking facilities make libraries more accessible to the public, encouraging diverse patronage and increasing community engagement.
-Libraries with better accessibility might be more willing to improve its facilities and might receive greater funding and community support, promoting the establishment of advanced facilities like DIHs.
+Libraries with better accessibility might be more willing to improve their facilities and might receive greater funding and community support, promoting the establishment of facilities like DIHs.
 
@@
 `year`: We hypothesize a negative relationship between years since built and the likelihood of having a DIH.
-Older libraries might lack modern infrastructure and technological resources necessary for a DIH, whereas recently built or renovated libraries are more likely to own technological innovations aligned with the concept of a DIH.
+Older libraries might lack the modern infrastructure and technological resources necessary for a DIH, whereas recently built or renovated libraries are more likely to own technological innovations aligned with the concept of a DIH.
 
@@
 Our model results are summarized in @tbl-model.
-The findings align with our prior expectations in some degree and provide insights into the relationship between the predictor variables and the presence of DIHs.
+The findings align with our prior expectations to some degree and provide clarity into the relationship between the predictor variables and the presence of DIHs.
 The intercept is negative, showing that more libraries do not have a DIH.
-The coefficient of `area` is 0, meaning the area of the library has litte effect on the outcome variable.
-The slope of `parking` and `workstations` are all positive, meaning a increase in them would lead to a higher likelihood of having DIHs.
+The coefficient of `area` is 0, meaning the area of the library has little effect on the outcome variable.
+The slope of `parking` and `workstations` are all positive, meaning an increase in them would lead to a higher likelihood of having DIHs.
 Rather, `year` has a negative slope, meaning older libraries are less likely to have a DIH, which aligns with our assumption.
@@
 The $R^2$ for this model is quite small, meaning the model might not fit the data well.
-However, the $RMSE$ is also quite small, meaning the problem of overfit would not present in our model.
+However, the $RMSE$ is also quite small, meaning the problem of overfitting would not be present in our model.
 More details are included in @sec-md.
@@
 
-## First discussion point
+## Review of the Analysis
 
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
+This paper investigates the factors influencing the presence of Digital Innovation Hubs (DIHs) in libraries.
+Libraries have evolved from being repositories of books to centers for community engagement, innovation, and technology access.
+DIHs are a relatively recent development in this transition, providing patrons with access to cutting-edge tools such as 3D printers, virtual reality systems, and other digital resources.
+However, the availability of DIHs is unevenly distributed, raising questions about what drives their presence in certain libraries but not others.
+Understanding these factors is important for policymakers, library administrators, and community planners aiming to promote equitable access to digital innovation.
 
-## Second discussion point
+To address this question, we used a logistic regression model to analyze library characteristics and their relationship with the likelihood of hosting a DIH.
+Specifically, we examined variables such as the size of the library (`area`), parking availability (`parking`), the number of workstations (`workstations`), and the library's age (`year`).
+These variables were chosen based on their potential relevance to the library’s capacity to support innovation and accessibility.
 
-Please don't use these as sub-heading labels - change them to be what your point actually is.
+Our analysis involved fitting a Bayesian logistic regression model, conducting diagnostic checks, and evaluating model performance using metrics such as $R^2$ and $RMSE$.
+This allowed us to identify significant relationships between library features and the presence of DIHs while accounting for potential model limitations.
+We supplemented the quantitative results with graphical analyses to visualize the effects of key variables, enhancing the interpretability of our findings.
 
-## Third discussion point
+By focusing on these specific predictors, this paper provides clarity into actionable factors that can inform decision-making for libraries considering establishing DIHs.
+Additionally, the methods and findings provide a framework for future research exploring the integration of technology in community spaces.
+This analysis offers a perspective on how infrastructure and resource allocation shape technological accessibility, highlighting both strengths and gaps in existing library systems.
 
-## Weaknesses and next steps
+## Physical Factors that Affect DIHs
 
-Weaknesses and next steps should also be included.
+One key outcome from this paper is the understanding of how library characteristics influence the likelihood of having a DIH.
+The logistic regression model shows that certain features - specifically parking availability, the number of workstations, and the library’s age - are significant predictors of whether a library will have a DIH.
+This suggests that libraries with more parking and a higher number of workstations are more likely to offer DIHs.
+
+From a broader perspective, this result shows how infrastructure and spatial resources can shape technological access.
+The availability of physical space for workstations and parking, for example, is not only a matter of practicality but may reflect deeper socio-economic factors, such as local investments in public services or the socio-economic status of the surrounding community.
+In particular, libraries located in areas with better parking availability and more resources may be better positioned to support digital hubs, thereby perpetuating a cycle of technological access in certain communities while excluding others.
+
+This has far-reaching implications for policymakers and community planners.
+It suggests that resource allocation in libraries—especially for digital services—should be carefully considered, as certain library features can serve as enablers or barriers to offering DIHs.
+For example, if policymakers wish to increase the availability of DIHs in underserved areas, they may need to address not only the availability of technology and funding but also the structural features of libraries that make them suitable for innovation.
+
+## Relationship between Newness and DIHs
+
+Another outcome from this paper is the relationship between a library’s age and its ability to adapt to modern technological demands.
+The negative relationship between the age of a library and the presence of a DIH shows that older libraries are less likely to adopt or host such innovations.
+This finding may reflect several underlying factors, including outdated infrastructure, limited budgets for upgrades, or the prioritization of traditional library services over newer, technology-focused initiatives.
+
+This observation underscores an important challenge for public institutions: balancing the preservation of historical and cultural roles with the need to evolve in response to contemporary demands.
+Older libraries often serve as community anchors, rich with history and traditional resources, but they may face structural or bureaucratic hurdles that hinder their ability to incorporate new technologies.
+The costs of retrofitting older buildings to accommodate high-tech equipment, coupled with limited funding or resistance to change, can create barriers to modernization.
+
+At a broader societal level, this finding highlights disparities in access to modern technology based on geographic and temporal factors.
+Communities served by older libraries may lack exposure to the benefits of DIHs, such as digital skills training or government support.
+This suggests that age-related disparities in library infrastructure could contribute to wider digital divides, limiting opportunities for communities that rely on these institutions as a primary source of technological access and education.
+
+Understanding this dynamic has implications for policymakers and library administrators.
+Investments in updating or redesigning older libraries could help narrow the gap and ensure that these facilities can continue to meet the evolving needs of their communities.
+Additionally, this suggest a need for targeted funding and support programs that help older libraries transition to more modern service models, preserving their historical value while enabling them to serve as hubs for digital innovation.
+
+## Limitations
+
+While this study provides clarity into the factors influencing the presence of DIHs in libraries, several limitations must be acknowledged to provide a balanced perspective.
+
+### Modeling Limitations
+
+The logistic regression model used in this analysis offers a simplified representation of the complex factors influencing the establishment of DIHs.
+The low $R^2$ value indicates that a significant proportion of the variation in DIH presence remains unexplained by the variables included in the model.
+While this highlights the importance of the variables analyzed, it also suggests that other factors, such as community demand, administrative priorities, or external funding, were not captured.
+
+### Data Constraints
+
+The dataset used in this study may have its inherent limitations.
+For instance, the data reflects a single snapshot in time, preventing the analysis of trends or temporal changes.
+Additionally, some variables, such as the year the library was built or the number of parking spaces, may serve as proxies rather than direct measures of a library's capacity to innovate.
+The lack of direct data on factors like community engagement, staff expertise, or budgetary allocations limits the model's ability to explain of DIH adoption.
+
+### Generalizability
+
+The study focuses on libraries within Toronto, which could limit the generalizability of the findings.
+For example, cultural, economic, and policy differences in other regions might lead to different relationships between the predictors and the presence of DIHs.
+Libraries in urban areas may face challenges distinct from those in rural areas, such as space constraints, differing user demographics, or funding opportunities, which are not explicitly addressed in this model.
+
+### Assumptions
+
+The logistic regression model assumes a normal distribution of predictor variables, and linear relationships between the predictors and the presence of a DIH, which may oversimplify the real-world dynamics.
+Non-normal distribution or non-linear relationships were not explored, potentially omitting clarity.
+
+## Future Steps
+
+This study provides a foundational understanding of the structural factors influencing the adoption of DIHs in libraries.
+However, several important questions remain unanswered, and future research should aim to narrow these gaps to enhance the understanding of the topic.
+
+### Incorporating Qualitative Factors
+
+While this study focused on structural features such as parking spaces, workstations, and the age of the library, the role of qualitative factors remains unexplored.
+Future research should investigate how variables like community engagement, staff expertise, and administrative priorities influence DIH adoption.
+Surveys or interviews with library staff and patrons could uncover the motivations, challenges, and strategies behind establishing DIHs, providing richer context beyond what structural data can offer.
+
+### Examining External Influences
+
+The impact of external influences, such as local government policies, regional funding availability, and partnerships with private organizations, should be investigated further.
+Understanding how these factors interact with the library's internal features could show additional pathways to fostering innovation.
+
+### Temporal Trends and Evolution
+
+This analysis used a cross-sectional dataset, which limits the ability to capture changes over time.
+Longitudinal studies would allow researchers to examine how libraries adapt to technological advancements and shifting community needs.
+
+### Understanding User Outcomes
+
+While this study focused on the factors that influence the presence of DIHs, future research should assess the outcomes for library users.
+Do DIHs improve digital literacy in the community?
+How do they impact job training, education, or access to technology in underserved areas?
+Evaluating these outcomes would help stakeholders understand the broader societal value of DIHs and justify further investment in their establishment.
+
+### Exploring Regional and Cultural Differences
+
+Given that this study's findings are limited to Toronto, future research should explore cultural and regional differences in DIH adoption.
+International comparisons could uncover how varying economic, cultural, and policy contexts shape the adoption and success of DIHs.
+Similarly, libraries in rural areas might face different challenges and opportunities compared to those in urban centers.
 
@@
 All predictor variables are right-skewed (@fig-area, @fig-parking, and @fig-workstations), except `year` (@fig-year).
-`year` might follows a normal distribution, while other predictor variables might follows an exponential distribution.
+`year` might follow a normal distribution, while other predictor variables might follow an exponential distribution.
 
@@
 
-The distribution of posterior is shown in @fig-posterior, which aligns with the actual data. From the graph, we can see that more libraries does not have a DIH.
+The distribution of the posterior is shown in @fig-posterior, which aligns with the actual data. From the graph, we can see that more libraries do not have a DIH.
 
@@
 From @fig-area-dih, we could see that smaller libraries are likely to have no DIHs, while larger libraries are not sure to have DIHs.
-In @fig-parking-dih and @fig-workstations-dih, libraries with more parking spaces and workstations tends to have a DIH.
+In @fig-parking-dih and @fig-workstations-dih, libraries with more parking spaces and workstations tend to have a DIH.
 On the opposite, the pattern shown in @fig-year-dih tells us older libraries tend to have no DIH.

### 2024-12-03 scripts/02-download_data.R
Fixed Code Style

@@ -19,12 +19,14 @@ package <- show_package("f5aa9b07-da35-45e6-b31f-d6790eb9bd9b")
 # get all resources for this package
 resources <- list_package_resources("f5aa9b07-da35-45e6-b31f-d6790eb9bd9b")
 
-# identify datastore resources; by default, Toronto Open Data sets datastore resource format to CSV for non-geospatial and GeoJSON for geospatial resources
-datastore_resources <- filter(resources, tolower(format) %in% c('csv', 'geojson'))
+# identify datastore resources; by default, Toronto Open Data sets datastore
+# resource format to CSV for non-geospatial and GeoJSON for geospatial resources
+datastore_resources <-
+  filter(resources, tolower(format) %in% c("csv", "geojson"))
 
 # load the first datastore resource as a sample
-raw_data <- filter(datastore_resources, row_number()==1) |> get_resource()
+raw_data <- filter(datastore_resources, row_number() == 1) |> get_resource()
 
 
 #### Save data ####
-write_csv(raw_data, "data/01-raw_data/raw_data.csv") 
+write_csv(raw_data, "data/01-raw_data/raw_data.csv")

### 2024-12-03 scripts/05-model_data.R

@@ -1,5 +1,5 @@
 #### Preamble ####
-# Purpose: Setup a linear model to describe the relationship between facilities 
+# Purpose: Setup a linear model to describe the relationship between facilities
 #   and area of Toronto libraries.
 # Author: Yanzun Jiang
 # Date: 25 November 2024
@@ -19,13 +19,15 @@ data <- read_parquet("data/02-analysis_data/analysis_data.parquet")
 
 
 ### Model data ####
-model <- stan_glm(
-    formula = dih ~ area + parking + workstations + year,
-    data = data,
-    family = binomial(link = "logit"),
-    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    seed = 1125)
+model <-
+  stan_glm(formula = dih ~ area + parking + workstations + year,
+           data = data,
+           family = binomial(link = "logit"),
+           prior =
+           normal(location = 0, scale = 2.5, autoscale = TRUE),
+           prior_intercept =
+           normal(location = 0, scale = 2.5, autoscale = TRUE),
+           seed = 1125)
 
 
 #### Save model ####

### 2024-12-04 paper/paper.qmd
Fixed Code Style
Survey Appendix Completed

@@
 
-data <- read_parquet(
-  here::here("data/02-analysis_data/analysis_data.parquet"))
+data <-
+  read_parquet(here::here("data/02-analysis_data/analysis_data.parquet"))
 ```
@@
 
+# Survey, Sampling, and Observational Data
+
+This study relies on observational data to examine the determinants of DIH presence in libraries.
+While observational data are useful, it is prone to biases and limitations that may affect the validity of conclusions.
+Some methodological improvements focusing on credible data collection, rigorous sampling, and thoughtful use of survey methods could be made to ensure robust and generalizable findings.
+
+## Observational Data Challenges
+
+Observational data often reflects phenomena in the real world but is susceptible to selection bias, confounding variables, and measurement errors.
+For example, in this study, libraries without detailed reporting may be underrepresented, skewing the analysis toward better-documented institutions.
+Also, variables such as "workstations" or "parking" might act as proxies for broader socioeconomic factors, but these relationships are not directly observed.
+
+## Idealized Methodology for Data Collection
+
+### Stratified Sampling
+
+Libraries could be stratified by key characteristics such as region, funding, and community size to mitigate biases and improve representativeness.
+Within each stratum, random sampling ensures proportional representation while reducing over-sampling in areas with higher reporting frequency.
+
+### Longitudinal Data Collection
+
+A cross-sectional approach only captures a single point in time.
+However, transitioning to a longitudinal design would enable us to observe how changes in library resources impact DIH presence over time and establish causality between predictors and outcomes.
+
+### Survey Design
+
+Although the data was obtained directly from the libraries, we could still design a survey to collect data.
+A carefully designed survey could gather valid data.
+Some approaches include using simple, jargon-free questions with clear response options, starting with general questions and moving to specifics, and retesting questions to ensure reliability and consistency across diverse respondents.
+
+## Simulation for Missing Data
+
+Missing or incomplete data often plagues observational studies.
+A simulation approach could impute missing values based on observed distributions of similar libraries and model the impact of missing data to assess potential biases in conclusions.
+
+## Sample Pollster
+
+We are conducting a survey to understand the factors influencing the presence of Digital Innovation Hubs (DIHs) in libraries.
+The information you provided will help shape policies and strategies to enhance library services nationwide.
+This survey will take approximately 5 minutes to complete.
+All responses will remain confidential and will only be used for academic research purposes.
+
+If you have any questions about the survey, please contact Yanzun Jiang at [yanzun.jiang@mail.utoronto.ca](mailto:yanzun.jiang@mail.utoronto.ca). Thank you for your participation!
+
+1. What is the name of your library?
+
+2. How many full-time staff members does your library employ?
+   - [ ] 1-5
+   - [ ] 6-10
+   - [ ] 11-20
+   - [ ] More than 20
+
+3. Does your library have a Digital Innovation Hub?
+   - [ ] Yes
+   - [ ] No
+
+4. If no, are there plans to establish a Digital Innovation Hub in the future?
+   - [ ] Yes, within the next year
+   - [ ] Yes, within the next 5 years
+   - [ ] No current plans
+
+5. What year was the library established?
+
+6. What is the approximate size of your library's main facility (in square feet)?
+
+7. How many computer workstations are available for public use in your library?
+
+8. Does your library provide parking for visitors?
+    - [ ] Yes
+    - [ ] No
+
+9. For this question, please choose Apple.  
+    - [ ] Apple
+    - [ ] Orange
+    - [ ] Banana
+    - [ ] Peach
+
+10. Which of the following services does your library currently offer? (Select all that apply)
+    - [ ] 3D printing
+    - [ ] Virtual reality equipment
+    - [ ] Coding workshops
+    - [ ] Audio/visual production tools
+    - [ ] Robotics and electronics kits
+    - [ ] Other (please specify):
+
+12. How would you rate your library’s funding for digital services?
+    - [ ] Excellent
+    - [ ] Good
+    - [ ] Fair
+    - [ ] Poor
+
+13. What challenges does your library face in implementing or maintaining a Digital Innovation Hub? (Select all that apply)
+    - [ ] Lack of funding
+    - [ ] Lack of skilled staff
+    - [ ] Limited space
+    - [ ] Insufficient community interest
+    - [ ] Other (please specify):
+
+14. Would you like your response to be included in a study?
+    - [ ] Yes
+    - [ ] No
+
+15. (Optional) Please share any additional comments or suggestions about Digital Innovation Hubs in libraries:
+
+Thank you for completing this survey! We appreciate your time and suggestions.
+
 \newpage
